WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-14 paper/ms.tex
grammar-hammer

%TODO: final numbers. note epoch changes...
The difference in $\chi^2$ between the linear and quadratic fit
corresponds to $p \approx 10^{-26}$.  A more likely possibility is
clearly that a systematic error is affecting one of the most important
sets of times: either the earliest times, the Huitson et al.\ Gemini
times (epoch numbers 30, 308, 577, and 837), or the TESS times.  We
have taken every precaution against systematic offsets in the TESS
times (Appendix~\ref{sec:verify_tess}), and Huitson et al.\ stand by
their reported times (J.-M. D\'esert, priv.\
comm.)\footnote{\citet{huitson_gemini_2017} corrected the times to be
at mid-exposure. They also analyzed other hot Jupiters, which all
showed mid-transit times as expected from a constant ephemeris.}.
Since the linear model provides a poor fit to the data, we discard it
from further consideration.

@@

If we instead assume the precession model, the best-fit eccentricity
is
\begin{equation}
  e = (1.83^{+ 1.88}_{- 0.75})\times10^{-3}
\end{equation}
The longitude of periapse correspondingly advances by $\dot{\omega} =
14.0^{+4.9}_{-3.5}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period would be $26^{+9}_{-7}$ years.

>>>>

%TODO: final numbers. note epoch changes...
The difference in $\chi^2$ between the linear and quadratic fit
corresponds to $p \approx 10^{-26}$.  A more likely possibility is
clearly that a systematic error is affecting one of the most important
sets of times: either the earliest times, the Huitson et al.\ Gemini
times (epoch numbers 30, 308, 577, and 837), or the TESS times.  We
have taken every precaution against systematic offsets in the TESS
times (Appendix~\ref{sec:verify_tess}), and Huitson et al.\ stand by
their reported times (J.-M. D\'esert, priv.\
comm.)\footnote{\citet{huitson_gemini_2017} corrected the times to be
at mid-exposure. They also analyzed other hot Jupiters, which all
showed mid-transit times as expected from a constant ephemeris.
The two Spitzer transits at epochs 362 and 365 are in independent
agreement with the Gemini times.}.
Since the linear model provides a poor fit to the data, we discard it
from further consideration.

@@

If we instead assume the precession model, the best-fit eccentricity
is
\begin{equation}
  e = (1.83^{+ 1.88}_{- 0.75})\times10^{-3}
\end{equation}
The longitude of periapse correspondingly advances by $\dot{\omega} =
14.0^{+4.9}_{-3.5}\ {\rm degrees}\,{\rm yr}^{-1}$, and the precession
period is $26^{+9}_{-7}$ years.
